Forecasting U.S. Presidential Election Outcomes: A Poll-Based Predictive Model Using YouGov Data

### 2024-11-03 paper/paper.qmd
Style code with styler.

library(tidyverse)
library(rstanarm)
library(modelsummary)
library(kableExtra)
library(arrow)

```

@@

ggplot(analysis_data, aes(x = party, y = pct, fill = party)) +
  geom_boxplot(alpha = 0.8) +
  scale_fill_brewer(palette = "Set1") +
  theme_minimal() +
  labs(x = "Political Party", y = "Predicted Vote Percentage")

```

@@

ggplot(analysis_data, aes(x = sample_size, y = pct)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Sample Size", y = "Predicted Vote Percentage")

```

@@

ggplot(analysis_data, aes(x = party, fill = party)) +
  geom_bar(alpha = 0.8) +
  scale_fill_brewer(palette = "Set1") +
  theme_minimal() +
  labs(x = "Political Party", y = "Number of Polls")

```

@@

# Load the model
first_model <- readRDS(file = here::here("models/final_model.rds"))

```

@@

modelsummary::modelsummary(
  list(
    "Vote Share Prediction Model" = first_model
  ),
  statistic = "mad",  # Mean absolute deviation
  fmt = 2  # Format to 2 decimal places
)%>%
  kableExtra::kable_styling(font_size = 8, full_width = TRUE)
```

@@

ggplot(analysis_data, aes(x = sample_size, y = pct)) +
  geom_point(alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  theme_minimal() +
  labs(x = "Sample Size", y = "Predicted Vote Percentage")

```

@@

ggplot(analysis_data, aes(x = party, y = pct, fill = party)) +
  geom_boxplot(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Political Party", y = "Predicted Vote Percentage")

```
In @fig-party-vote, the distribution of predicted vote percentages by political party is shown. The model indicates that Republican candidates generally receive a higher predicted vote share compared to Democratic candidates. Third-party candidates, such as those from the Green and Independent parties, tend to have significantly lower predicted vote percentages.

>>>>

library(tidyverse)
library(rstanarm)
library(modelsummary)
library(kableExtra)
library(arrow)
```

@@

ggplot(analysis_data, aes(x = party, y = pct, fill = party)) +
  geom_boxplot(alpha = 0.8) +
  scale_fill_brewer(palette = "Set1") +
  theme_minimal() +
  labs(x = "Political Party", y = "Predicted Vote Percentage")
```

@@

ggplot(analysis_data, aes(x = sample_size, y = pct)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Sample Size", y = "Predicted Vote Percentage")
```

@@

ggplot(analysis_data, aes(x = party, fill = party)) +
  geom_bar(alpha = 0.8) +
  scale_fill_brewer(palette = "Set1") +
  theme_minimal() +
  labs(x = "Political Party", y = "Number of Polls")
```

@@

# Load the model
first_model <- readRDS(file = here::here("models/final_model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "Vote Share Prediction Model" = first_model
  ),
  statistic = "mad", # Mean absolute deviation
  fmt = 2 # Format to 2 decimal places
) %>%
  kableExtra::kable_styling(font_size = 8, full_width = TRUE)
```

@@

ggplot(analysis_data, aes(x = sample_size, y = pct)) +
  geom_point(alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  theme_minimal() +
  labs(x = "Sample Size", y = "Predicted Vote Percentage")
```

@@

ggplot(analysis_data, aes(x = party, y = pct, fill = party)) +
  geom_boxplot(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Political Party", y = "Predicted Vote Percentage")
```
In @fig-party-vote, the distribution of predicted vote percentages by political party is shown. The model indicates that Republican candidates generally receive a higher predicted vote share compared to Democratic candidates. Third-party candidates, such as those from the Green and Independent parties, tend to have significantly lower predicted vote percentages.
